Attribute fusion in a latent process model for time series of graphs

### 2011-05-18 ssp2011.tex
State the power estimate for num triangle

\documentclass[draftcls]{IEEEtran}

@@

\usepackage{mathrsfs}

@@

\usepackage{cite}

@@

behaviour in an otherwise stationary setting as depicted in Fig.~\ref{fig:notional_change_point}. 

@@

  \caption{Notional depiction of the problem of change-point detection in a time-series of graphs}

@@

$\mathcal{E}$, number of triangles $\tau_{\lambda}$, scan $\Psi$, and
max degree $\Delta$. Specifically, we consider linear attribute
fusion with parameter $\lambda \in \mathbb{R}^{K}$ via

@@

  \mathcal{E}_{\lambda}(G(t)) = \sum_{k=1}^{K} \lambda_k \sum_{u,v}
  \mathbb{I}\{ \phi(uv,t) = k \} \\
  \tau_\lambda(G(t)) = \sum_{k=1}^{K} \lambda_k \!\! \sum_{(u,v,w) \in
    \binom{V}{3}} h_k(u,v,w) \\
  \Delta_{\lambda}(G(t)) = \max_{v \in V} \, \sum_{k = 1}^{K} \lambda_k
  \sum_{u \in N(v)}{\mathbb{I}\{\phi(uv,t) = k\}} \\

@@

  \Psi_{\lambda}(G(t)) = \max_{v \in V} \sum_{k = 1}^{K}
  \lambda_k \!\!\sum_{u,w \in N(v)}\!\!\! \mathbb{I}\{\phi(uw,t) = k\} 
where $h_k(u,v,w)$ is the indicator function that the argument, a set
of three vertices, forms a triangle of type $k$. A triangle
is of type $k$ provided that all edges in the triangle have attribute
$k$. \\ \\
Let $J_{\lambda}(t)$ be a statistic of the form as in Eq.~\eqref{eq:6} through
Eq.~\eqref{eq:3}. We define the normalization $\bar{J}^{l}_\lambda(t)$
of $J_{\lambda}$ based on recent past as

@@

\subsection{Power estimates for $\mathcal{E}_\lambda(t)$}

@@

\cite{lee:_laten_proces_model_time_attrib_random_graph} that for the
case where $J_\lambda(t)$ is $\mathcal{E}_{\lambda}(t)$, $T_{\lambda}^{l}(t)$ 

@@

@@

      \mathcal{G}(a_n \sigma_1 + \mu_1, b_n \sigma_1 ) & \text{for $t < t^{*}$.} \\
     \mathcal{G}(a_m \sigma_2 + \mu_2, b_m \sigma_2) &

@@

    \mu_1 &= (n-1)\langle \lambda, \pi_{00} \rangle \\
    \sigma_1 &= \sqrt{(n-1)\langle \lambda, \eta_{00} \lambda \rangle} \\
    \mu_2 &= \,\, (m - 1) \langle x, \pi_{11} \rangle + (n-

@@

    \\ \sigma_2 &= \sqrt{ (m - 1) \langle \lambda, \eta_{11} \lambda \rangle + (n -

@@

    \frac{\sqrt{\pi}}{6} \frac{\mu_2 - \mu_1 + a_m\sigma_2 - (a_n + b_n
      \gamma)\sigma_1}{b_n \sigma_1} & \text{if $t =

@@

    \frac{\sqrt{\pi} b_m \sigma_2}{6 b_n \sigma_1} & \text{if $t =

@@

once again determined by various factors, but the dominating factor is

@@

and $m$, we also have
  \frac{\rho_\lambda}{\varsigma_\lambda} &= (1 + o(1)) \frac{\mu_2 - \mu_1}{b_m
    \sigma_ 2} \\ &= \frac{\langle \lambda, (m-1)\pi_{11} + (n-m)\pi_{01} -

@@

delegated to the appendices. \\ \\

@@

the case where $t < t^{*}$ and for $t = t^{*}$. To aid the exposition,
we first introduce some notations. Let $\lambda^{(2)}$ be the
element-wise square of $\lambda$. Define $C_{00}$, $C_{01}$, $C_{11}$
and $p_{00}$, $p_{01}$, $p_{11}$ to be
  \label{eq:19}
  C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
    \pi_{00}\rangle}; \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle} \\
C_{11} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
    \pi_{11}\rangle}; \quad p_{11} = \tfrac{(\langle \lambda, \pi_{11}
    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{11} \rangle} \\
C_{10} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
    \pi_{10}\rangle}; \quad p_{10} = \tfrac{(\langle \lambda, \pi_{10}
    \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{10} \rangle} 
Also let $z_n$ be defined, for any $n \in \mathbb{N}$, by

@@

@@

    a_n &=  C_{00}p_{00}\tbinom{N_{0}}{2} \\ 
   b_n &= C_{00}p_{00} N_{0} \frac{\sigma_0}{\sqrt{2 \log

@@

We now move to the limiting distribution for $\Psi_{\lambda}(t^{*})$. 
Let us define $E$ and $F$ by
  E \sim \mathrm{Bin}(m-1, \langle \pi_{11}, 1 \rangle) \\ F \sim \mathrm{Bin}(n-m,
  \langle \pi_{01}, 1 \rangle)
For any random variable $X$, we let $\mu_X$ and $\sigma_X^{2}$ denote
the mean and variance of $X$. If $X$ and $Y$ are independent random
variables, we let $\mu_{X + Y}$ and $\sigma_{X + Y}^2$ denote the mean
and variance of the convolution $X + Y$. \\
\noindent Let $N_{\kappa}$ be the quantity defined by
  \label{eq:18}
  N_{\kappa} = \mu_{E + F} + z_m \sigma_{E + F}

@@

C_{00} p_{00} \tbinom{N_\kappa}{2} &+ (C_{11}p_{11} - C_{10} p_{10})
\tbinom{\mu_E}{2} \\ &+ (C_{01} p_{01} - C_{00} p_{00}) \mu_E \mu_F 

@@

    b_{n,m} = C_{00} p_{00} N_\kappa \frac{\sigma_{E + F}}{\sqrt{2

@@

\begin{proof}[Theorem \ref{thm:1}]

@@

\end{proof}
\begin{proof}[Proposition~\ref{prop:3}]
  Let $d_{\lambda}(v;t)$ be the (fused) degree of vertex $v$ at time
  $t$, i.e.,
    d_{\lambda}(v;t) = \sum_{k = 1}^{K} \lambda_k \sum_{w \in N(v)}
    \mathbb{I}\{ \phi(vw,t) = k \}
  Let $\Gamma^{(k)}(v;t) = |\{w \colon \mathbb{I}\{\phi(wv,t) =
  k\}|$. The vector $\bm{\Gamma}(v;t) = (\Gamma^{(k)}(v;t))_{k=1}^{K}$
  for $t < t^{*}$ is distributed as a multinomial with $n-1$ trials
  and probability vector $\pi_{00}$. The following statements are

@@

  $K$. Now $d_{\lambda}(v;t) = \langle \lambda, \bm{\Gamma}(v;t)
  \rangle$ and
  thus, by the central limit theorem, we have

@@

    among the $d_{\lambda}(v,t)$ can be ignored. $d_{\lambda}(v;t)$,
    when normalized, can thus be considered as a sequence of
    independent random variables from the standard normal in the
    limit. It is widely known that the sample maximum of standard
    normal random variables converges weakly to a Gumbel distribution
    \cite[\S 2.3]{galambos87:_asymp_theor_extrem_order_statis}. It is,
    however, not clear whether the convergence of
    $\Delta_{\lambda}(t)$ to a Gumbel distribution continues to hold
    under the composition of weak convergence as
    outlined above. We avoid this problem by showing
    directly that 

@@

    \rightarrow \infty$ and $u = O(\log{n})$, we have the

@@

\end{proof}
\begin{proof}[Lemma~\ref{lem:2}]

@@

\end{proof}
\begin{proof}[Theorem~\ref{thm:2}]

@@

\end{proof}
\begin{proof}[Theorem~\ref{thm:3}]

@@

\begin{proof}[Eq.~\eqref{eq:27}]

@@

\end{proof}
\begin{proof}[Eq.~\eqref{eq:28}]

@@

and once again, by a concentration inequality, we can show that m
$\mathbb{P}(M(v) = e, W(v) = f, \{e,f\} \in S_2) = o(1)$. As for

@@

@@

\end{proof}

\end{proof}
\bibliography{ssp2011}
\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:

>>>>

\documentclass[final]{IEEEtran}

@@

%\usepackage{mathrsfs}

@@

\usepackage[noadjust]{cite}

@@

behaviour in an otherwise stationary setting as depicted in
Fig.~\ref{fig:notional_change_point}.

@@

  \caption{Notional depiction of the problem of change-point detection
    in a time-series of graphs}

@@

$\mathcal{E}$, number of triangles $\tau$, scan $\Psi$, and
max degree $\Delta$. Let $G = (V,E,\phi)$ be an attributed graph with 
$\phi \colon \tbinom{V}{2} \mapsto \mathscr{K}_{+}$. For a given
$\{u,v\} \in \tbinom{V}{2}$, we define a $\Gamma_{uv} \in
\mathbb{R}^{K+1}$ by $\Gamma_{uv}(k) = \mathbb{I}\{\phi(\{u,v\}) =
k\}$. Let $\widehat{\Gamma}_{uv}$ be the first $K$ coordinates of
$\Gamma_{uv}$. Thus $\widehat{\Gamma}_{uv} = \bm{0}$ unless $\{u,v\}
\in E$. Under the independent edges assumption, the
$\Gamma_{uv}$ are independent, and hence the $\widehat{\Gamma}_{uv}$
are also independent. We can consider linear attribute fusion of graph invariants with
parameter $\lambda \in \mathbb{R}^{K}$ via
%\begin{gather}
%  \label{eq:6}
%  \mathcal{E}_{\lambda}(G) = \sum_{k=1}^{K} \lambda_k \sum_{u,v}
%  \mathbb{I}\{ \phi(uv) = k \} \\
%  \tau_{\lambda}(G) = \sum_{(i,j,k) \in K^{3}\vphantom{\tbinom{V}{3}}}
%  \, \, \sum_{(u,v,w)
%      \in \tbinom{V}{3}} \lambda_{i}\lambda_j \lambda_k h_{ijk}(u,v,w) \\
%  \Delta_{\lambda}(G) = \max_{v \in V} \, \sum_{k = 1}^{K} \lambda_k
%  \sum_{u \in N(v)}{\mathbb{I}\{\phi(\{u,v\}) = k\}} \\
%  \label{eq:3}
%  \Psi_{\lambda}(G) = \max_{v \in V} \sum_{k = 1}^{K}
%  \lambda_k \!\!\sum_{u,w \in N(v)}\!\!\! \mathbb{I}\{\phi(\{u,w\}) = k\} 
%  \end{gather}

@@

  \mathcal{E}_{\lambda}(G) &= \sum_{\mathclap{\{u,v\} \in
      \tbinom{V}{2}}} \langle
  \lambda, \widehat{\Gamma}_{uv} \rangle \\
  \tau_{\lambda}(G) &= \sum_{\mathclap{\{u,v,w\} \in \tbinom{V}{3}}} \langle
  \lambda, \widehat{\Gamma}_{uv} \rangle \langle \lambda,
  \widehat{\Gamma}_{uw} \rangle \langle \lambda, \widehat{\Gamma}_{vw}
  \rangle \\ 
\Delta_{\lambda}(G) &= \max_{v \in V} \, \sum_{w \in N(v)} \langle
\lambda, \widehat{\Gamma}_{vw} \rangle \\

@@

  \Psi_{\lambda}(G) &= \max_{v \in V} \sum_{u,w \in N(v)} \langle
  \lambda, \widehat{\Gamma}_{uw} \rangle
  Let $\{G(t)\}$ be a time series of graphs. Let $J_{\lambda}(t)$ be a
  statistic for $G(t)$ of the form as in Eq.~\eqref{eq:6} through
  Eq.~\eqref{eq:3}. We define the normalization
  $\bar{J}^{l}_\lambda(t)$ of $J_{\lambda}$ based on recent past as

@@

\subsection{Power estimates for $\mathcal{E}_\lambda$}

@@

\cite{lee:_laten_proces_model_time_attrib_random_graph} that if
$J_\lambda(t) = \mathcal{E}_{\lambda}(G(t))$, then $T_{\lambda}^{l}(t)$ 

@@

\subsection{Power estimates for $\tau_{\lambda}$}
\label{sec:power-estim-tau_l}
The limiting distribution for the number of triangles in unattributed
\cite{nowicki88:_subgr_u_statis_method} for the Erd\"{o}s-Renyi 
and in \cite{rukhin09:_asymp_analy_various_statis_random_graph_infer}
for the kidney-egg model. We note here the small changes that allow us
to extend the results in
\cite{rukhin09:_asymp_analy_various_statis_random_graph_infer,%
nowicki88:_subgr_u_statis_method}
to our attributed graphs model. Let $Y_{uv} = \langle \lambda,
\widehat{\Gamma}_{uv} \rangle$ for $\{u,v\} \in \tbinom{V(t)}{2}$. We
can now write $\tau_{\lambda}(G(t))$ as
  \label{eq:45}
  \frac{\tau_{\lambda}(G(t))}{\tbinom{n}{3}} &= \tbinom{n}{3}^{-1}
  \sum_{\mathclap{\{u,v,w\} \in \tbinom{V}{3}}} Y_{uv} Y_{uw} Y_{vw}
  \\ &= \tbinom{n}{3}^{-1}
  \sum_{\mathclap{\{e_1, e_2, e_3\} \in \tbinom{E(t)}{3}}} Y_{e_1}
  Y_{e_2} Y_{e_3}
$\tau_{\lambda}(G(t))/\tbinom{n}{3}$ is then an (incomplete)
$U$-statistic on $\{Y_{e}\}$, with kernel function $h(Y_{1}, Y_{2},
Y_{3}) = Y_{1} Y_{2} Y_{3}$. By using Hajek's projection method, we
can show that $\tau_{\lambda}(G(t))$ converges to a normal
distribution as $n \rightarrow \infty$. 
  \label{lem:3}
  Let $\tau_{\lambda}^{*}$ be the Hajek's projection of $\tau_{\lambda}$, i.e.,
  \label{eq:46}
  \tau_{\lambda}^{*}(G(t)) = \sum_{e \in E(t)} \mathbb{E}[
  \tau_{\lambda}(G(t)) \, \lvert \, Y_{e}]
For $t < t^{*}$, we have
  \mu_0 = \mathbb{E}[\tau_{\lambda}^{*}(G(t))] &= \tbinom{n}{3} \langle 
  \lambda, \pi_{00} \rangle^{3} \\
  \sigma_0 = \sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]} &= (n-2) \langle \lambda,
  \pi_{00} \rangle^{2} \sqrt{\tbinom{n}{2} \langle \lambda, \eta_{00}
  \lambda \rangle}
For $t = t^{*}$, we have
    \label{eq:42}
    \mu_A = \mathbb{E}[\tau_{\lambda}^{*}(G(t))] = \tbinom{m}{3}
    \langle \lambda, \pi_{11} \rangle^{3} &+
    \tbinom{m}{2}(n-m) \langle \lambda, \pi_{11} \rangle \langle
    \lambda, \pi_{01} \rangle^{2} \\ &+ m \tbinom{n-m}{2} \langle \lambda,
    \pi_{01} \rangle^{2} \langle \lambda, \pi_{00} \rangle \\ &+
    \tbinom{n-m}{3} \langle \lambda, \pi_{00} \rangle^{3}
    \sigma_A^{2} = \mathrm{Var}[\tau_{\lambda}^{*}(G(t))] = \tbinom{m}{2} \langle \lambda, \eta_{11} \lambda
    \rangle S_1  
    &+ m(n-m) \langle \lambda, \eta_{01} \lambda \rangle S_2  \\
    &+ \tbinom{n-m}{2} \langle \lambda, \eta_{00} \lambda \rangle S_3
  where $S_1$, $S_2$, and $S_3$ are given by
    S_1 &= \Bigl[(m-2) \langle \lambda, \pi_{11} \rangle^{2} + (n-m)
    \langle \pi_{01} \rangle^{2} \Bigr]^{2} \\ 
    S_2 &= \Bigl[(m-1)
    \langle \lambda, \pi_{11} \rangle \langle \lambda, \pi_{01}
    \rangle + (n-m-1) \langle \lambda, \pi_{00} \rangle \langle
    \lambda, \pi_{01} \rangle \Bigr]^{2} \\
    S_3 &= \Bigl[m \langle \lambda, \pi_{01} \rangle^{2} + (n-m-2) \langle
    \lambda, \pi_{00} \rangle^{2} \Bigr]^{2} 
  As $n \rightarrow \infty$ and $m = \Omega(\sqrt{n})$, we have
    \label{eq:49}
    \frac{\tau_{\lambda}(t) -
      \mathbb{E}[\tau_{\lambda}^{*}(G(t))]}{\sqrt{\mathrm{Var}[\tau_{\lambda}^{*}(G(t))]}}
From Lemma~\ref{lem:3}, we can show that the limiting distribution of
$T_{\lambda}^{l}(t)$ is, once again, a Student t-distribution with
$l-1$ degrees of freedom.
  \label{thm:5}
  \mathbb{R}^{K}$. Define the random varialbel $\psi_{\lambda}^{l}(t)$
    \label{eq:50}
    \psi_{\lambda}^{l}(t) = \begin{cases}
      \Bigl(\sqrt{\tfrac{l}{l+1}}\,\Bigr) T_{\lambda}^{l}(t) & \text{if $t <
      \Bigl(\sqrt{\tfrac{l \sigma_0^{2}}{l \sigma_A^{2} + \sigma_0^{2}} }\,\Bigr)
      T_{\lambda}^{l}(t) & \text{if $t = t^{*}$}
  As $n \rightarrow \infty$, $\psi_{\lambda}^{l}(t)$ converges to a Student $t$-distribution with $l - 1$ degrees of freedom and
  non-centrality parameter $\mu_{\lambda}$ where
    \label{eq:51}
    \mu_{\lambda} = \begin{cases} 0 & \text{if $t < t^{*}$} \\
      \frac{\mu_A - \mu_0}{\sqrt{l \sigma_A^{2} + \sigma_0^{2}}} &
       \text{if $t = t^{*}$}
The power approximation for $\tau_{\lambda}$ is determined by various
factors, but similar to the power approximation for
$\mathcal{E}_{\lambda}$, the dominating factor is likely to be
  $\mu_\lambda$. Thus, we are also interested in finding the $\lambda$
  that will maximize $\mu_\lambda$. However, because of the high power
  of $\lambda$ in the expression for $\mu_{\lambda}$, an analytic
  solution to $\argmax_{\lambda}{\mu_{\lambda}}$ might not be possible.

@@

      \mathcal{G}(a_n \sigma_0 + \mu_0, b_n \sigma_0 ) & \text{for $t < t^{*}$.} \\
     \mathcal{G}(a_m \sigma_A + \mu_A, b_m \sigma_A) &

@@

    \mu_0 &= (n-1)\langle \lambda, \pi_{00} \rangle \\
    \sigma_A &= \sqrt{(n-1)\langle \lambda, \eta_{00} \lambda \rangle} \\
    \mu_0 &= \,\, (m - 1) \langle x, \pi_{11} \rangle + (n-

@@

    \\ \sigma_A &= \sqrt{ (m - 1) \langle \lambda, \eta_{11} \lambda \rangle + (n -

@@

    \frac{\sqrt{\pi}}{6} \frac{\mu_A - \mu_0 + a_m\sigma_A - (a_n + b_n
      \gamma)\sigma_0}{b_n \sigma_0} & \text{if $t =

@@

    \frac{\sqrt{\pi} b_m \sigma_A}{6 b_n \sigma_0} & \text{if $t =

@@

determined by various factors, but the dominating factor is

@@

and $m$, we have
  \frac{\rho_\lambda}{\varsigma_\lambda} &= (1 + o(1)) \frac{\mu_A - \mu_0}{b_m
    \sigma_A} \\ &= \frac{\langle \lambda, (m-1)\pi_{11} + (n-m)\pi_{01} -

@@

relegated to the appendices. \\ \\

@@

the cases when $t < t^{*}$ and $t = t^{*}$. To aid the exposition,
 we first introduce some notations. Let $z_n$ be defined, for $n \in \mathbb{N}$, by

@@

Let us also define $E$ and $F$ by
  E \sim \mathrm{Bin}(m-1, \langle 1, \pi_{11} \rangle) \\ F \sim \mathrm{Bin}(n-m,
  \langle 1, \pi_{01} \rangle)
Let $E + F$ be the convolution of $E$ and $F$. Denote by $\mu_{E+F}$ and
$\sigma_{E+F}^{2}$ the mean and variance of $E + F$. Finally, let
$N_{\kappa} = \mu_{E + F} + z_m \sigma_{E + F}$. We then have the
following results.
%Let $\lambda^{(2)}$ be the
% element-wise square of $\lambda$. Define $C_{00}$, $C_{01}$, $C_{11}$
% and $p_{00}$, $p_{01}$, $p_{11}$ to be
% \begin{gather}
%   \label{eq:19}
%   C_{00} = \tfrac{\langle \lambda^{(2)}, \pi_{00} \rangle}{\langle \lambda,
%     \pi_{00}\rangle}; \quad p_{00} = \tfrac{(\langle \lambda, \pi_{00}
%     \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{00} \rangle} \\
% C_{11} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
%     \pi_{11}\rangle}; \quad p_{11} = \tfrac{(\langle \lambda, \pi_{11}
%     \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{11} \rangle} \\
% C_{10} = \tfrac{\langle \lambda^{(2)}, \pi_{11} \rangle}{\langle \lambda,
%     \pi_{10}\rangle}; \quad p_{10} = \tfrac{(\langle \lambda, \pi_{10}
%     \rangle)^{2}}{\langle \lambda^{(2)},\, \pi_{10} \rangle} 
% \end{gather}

@@

    a_n &=  \langle \lambda, \pi_{00} \rangle \tbinom{N_{0}}{2} \\ 
   b_n &= \langle \lambda, \pi_{00} \rangle N_{0} \frac{\sigma_0}{\sqrt{2 \log

@@

@@

\langle \lambda, \pi_{00} \rangle \tbinom{N_\kappa}{2} &+
\langle \lambda, \pi_{11} - \pi_{00} \rangle
\tbinom{\mu_E}{2} \\ &+ \langle \lambda, \pi_{01} - \pi_{00} \rangle \mu_E \mu_F 

@@

    b_{n,m} = \langle \lambda, \pi_{00} \rangle N_\kappa \frac{\sigma_{E + F}}{\sqrt{2

@@

\begin{IEEEproof}[Theorem \ref{thm:1}]

@@

\end{IEEEproof}
\begin{IEEEproof}[Proposition~\ref{prop:3}]
  Let $v \in V(t)$ and denote by $d_{\lambda}(v;t)$ the (fused) degree
  of vertex $v$, i.e.,
    d_{\lambda}(v;t) = \sum_{w \in N(v)} \langle \lambda,
    \widehat{\Gamma}_{vw} \rangle
  For $t < t^{*}$, each of the $\widehat{\Gamma}_{vw}$ is a multinomial
  trial with probability vector $\pi_{00}$. The following statements are

@@

  $K$.  By the central limit theorem, we have

@@

    among the $\{d_{\lambda}(v;t)\}_{v \in V(t)}$ can be
    ignored. $d_{\lambda}(v;t)$, can thus be considered as a sequence
    of independent random variables from a normal distribution. It is
    widely known that the sample maximum of standard normal random
    variables converges weakly to a Gumbel distribution \cite[\S
    2.3]{galambos87:_asymp_theor_extrem_order_statis}. It is, however,
    not clear whether the convergence of $\Delta_{\lambda}(t)$ to a
    Gumbel distribution continues to hold under the composition of
    weak convergence as outlined above. We avoid this problem by
    showing directly that

@@

    \rightarrow \infty$ and $u = O(\sqrt{\log{n}})$, we have the

@@

\end{IEEEproof}
\begin{IEEEproof}[Lemma~\ref{lem:2}]

@@

\end{IEEEproof}
\begin{IEEEproof}[Theorem~\ref{thm:2}]

@@

\end{IEEEproof}
\begin{IEEEproof}[Theorem~\ref{thm:3}]

@@

\begin{IEEEproof}[Eq.~\eqref{eq:27}]

@@

\end{IEEEproof}
\begin{IEEEproof}[Eq.~\eqref{eq:30}]

@@

and once again, by a concentration inequality, we can show that $m
\mathbb{P}(M(v) = e, W(v) = f, \{e,f\} \in S_2) = o(1)$. As for

@@

    \label{eq:44}

@@

\end{IEEEproof}

\end{IEEEproof}
\bibliography{ssp2011}
\end{document}
%%% Local Variables: 
%%% mode: latex
%%% TeX-master: t
%%% End:
